Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
quotes opressoras

\begin{flushright}{\slshape
    {Before I came across it, I had read many articles describing intricate properties of neurons, the many varieties of neurotransmitters and second-messenger molecules, synaptic modification processes, complex and hypercomplex cells, columns in the visual cortex, and so on.  All of this was fascinating but seemed very biological and microscopic:  altogether quite distant from everyday mental experiences.  I simply had never come across a cogent theory that addressed brain mechanisms on a global level.  Pentti Kanerva's memory model was a revelation for me: it was the very first piece of research I had ever come across that made me feel I could glimpse the distant goal of understanding how the brain works as a whole. It gave me a concrete sense for how familiar mental phenomena could be thought of as distributed patterns of micro-events, thanks to beautiful mathematics.
	.} \\ \medskip
    --- Douglas Hofstadter}
\end{flushright}
\bigskip
\bigskip

>>>>

\begin{flushright}{\slshape
    {Before I came across it, I had read many articles describing intricate properties of neurons, the many varieties of neurotransmitters and second-messenger molecules, synaptic modification processes, complex and hypercomplex cells, columns in the visual cortex, and so on.  All of this was fascinating but seemed very biological and microscopic:  altogether quite distant from everyday mental experiences.  I simply had never come across a cogent theory that addressed brain mechanisms on a global level.  Pentti Kanerva's memory model was a revelation for me: it was the very first piece of research I had ever come across that made me feel I could glimpse the distant goal of understanding how the brain works as a whole. It gave me a concrete sense for how familiar mental phenomena could be thought of as distributed patterns of micro-events, thanks to beautiful mathematics.} \\ \medskip
    --- Douglas Hofstadter}
\end{flushright}
\bigskip
\bigskip

### 2018-03-14 Chapters/Chapter03.tex
quotes opressoras

The way innovations diffuse in the market is an important and useful topic in marketing, which was made popular through Rogers' work \citep{rogers1962diffusion} and has influenced many marketing researchers. Within innovation diffusion, \citet{bass1969} proposed a model which forecasts how many people will have adopted new products or technologies by a given point in time. INFORMS members have voted this model as one of the Top 10 Most Influential Papers published in the 50-year history of Management Science in connection with the 50th anniversary of the journal \citep{bass2004comments}.

>>>>

\bigskip

\begin{flushright}{\slshape
    {Why do entrepreneurs appear, not continuously, that is singly in every appropriately chosen interval, but in clusters? Exclusively because the appearance of one or a few entrepreneurs facilitates the appearance of others, and these the appearance of more, in ever-increasing numbers.}
	\\ \medskip
    --- Joseph Schumpeter}
\end{flushright}
\bigskip
\bigskip

The way innovations diffuse through markets is an important and useful topic in marketing, which was made popular through Rogers' work \citep{rogers1962diffusion} and has influenced many marketing researchers. Within innovation diffusion, \citet{bass1969} proposed a model which forecasts how many people will have adopted new products or technologies by a given point in time. INFORMS members have voted this model as one of the Top 10 Most Influential Papers published in the 50-year history of Management Science in connection with the 50th anniversary of the journal \citep{bass2004comments}.
